### 2016-09-30 notions.tex
GBF, adding descriptive names to theorem statements in Section 4

It is immediate that $\Pr[\ExpPrivSSreal{\setprim}{A'}=1] = \AdvPrivOW{\setprim,\mathcal{D}}{A}$.
But for any simulator $\Sim$,
the only information
that $\Sim$
and $A'$ jointly have in the ideal world
about the set~$S$ that was sampled is ${\sf leak}(S)$; thus,
\[\Prob{\ExpPrivSSsim{\setprim,{\sf leak}}{A', \Sim}=1} \leq
2^{-\tilde H_\infty({\cal D} \mid {\sf leak})}.\]
The theorem follows.
\end{proof}

@@

Note that we can express $\Prob{\ExpPrivSSreal{\setprim}{A}=1}$ as the probability that $A$
outputs~1 in
the following experiment~$G0$: \jnote{BTW, in class when I do this stuff I usually
say ``game'' and then correct myself and say ``\ldots but if you want to get funded,
call it an experiment.'' (Some light humor while you work.)}
\begin{enumerate}
\item $S \getsr A$.
\item $s_1, \ldots, s_t \getsr \Rep_1(S)$.
\item $K \getsr \bits^n$.
\item $\pubaux \getsr \Rep_2(|S|, F_k(s_1), \ldots, F_k(s_t))$.
\item Return $A(\pubaux)$.
\end{enumerate}

Now, consider an experiment $G1$ in which computation is done as follows:
\begin{enumerate}
\item $S \getsr A$.
\item $s_1, \ldots, s_t \getsr \Rep_1(S)$.
\item $y_1, \ldots, y_t \leftarrow \bits^{\ell_{out}}$
\item $\pubaux \getsr \Rep_2(|S|, y_1, \ldots, y_t)$.
\item Return $A(\pubaux)$.
\end{enumerate}
It is immediate that the difference between the probability that $A$ outputs~1 in
$G1$ and the probability that it outputs~1 in
$G0$ is bounded by ${\sf Adv}_F^{\rm PRF}(A')$, where $A'$ performs the
obvious simulation.

@@

One can observe that $G2$ is identical to the following experiment:
\begin{enumerate}
\item $S \getsr A$.
\item $\pubaux \getsr \Sim(|S|)$.
\item Return $A(\pubaux)$.
\end{enumerate}
Moreover, the probability with which $A$ outputs~1 in this experiment is
precisely $\Prob{\ExpPrivSSsim{\setprim,{\sf leak}}{A, \Sim}=1}$.
This completes the proof.
\end{proof}

>>>>

It is immediate that $\Pr[\ExpPrivSSreal{\setprim}{A'}=1] = \AdvPrivOW{\setprim,\mathcal{D}}{A}$.
But for any simulator $\Sim$,
the only information
that $\Sim$
and $A'$ jointly have in the ideal world
about the set~$S$ that was sampled is ${\sf leak}(S)$; thus,
\[\Prob{\ExpPrivSSsim{\setprim,{\sf leak}}{A', \Sim}=1} \leq
2^{-\tilde H_\infty({\cal D} \mid {\sf leak})}.\]
The theorem follows. \hfill\qed
\end{proof}

@@

Note that we can express $\Prob{\ExpPrivSSreal{\setprim}{A}=1}$ as the probability that $A$
outputs~1 in
the following experiment~$G0$: 
%\jnote{BTW, in class when I do this stuff I usually
%say ``game'' and then correct myself and say ``\ldots but if you want to get funded,
%call it an experiment.'' (Some light humor while you work.)}
\begin{enumerate}
\item $S \getsr A$.
\item $s_1, \ldots, s_t \getsr \Rep_1(S)$.
\item $K \getsr \bits^n$.
\item $\pubaux \getsr \Rep_2(|S|, F_k(s_1), \ldots, F_k(s_t))$.
\item Return $A(\pubaux)$.
\end{enumerate}

Now, consider an experiment $G1$ in which computation is done as follows:
\begin{enumerate}
\item $S \getsr A$.
\item $s_1, \ldots, s_t \getsr \Rep_1(S)$.
\item $y_1, \ldots, y_t \leftarrow \bits^{\ell_{out}}$
\item $\pubaux \getsr \Rep_2(|S|, y_1, \ldots, y_t)$.
\item Return $A(\pubaux)$.
\end{enumerate}
It is immediate that the difference between the probability that $A$ outputs~1 in
$G1$ and the probability that it outputs~1 in
$G0$ is bounded by $\AdvPRF{F}{A'}$, where $A'$ performs the
obvious simulation.

@@

One can observe that $G2$ is identical to the following experiment:
\begin{enumerate}
\item $S \getsr A$.
\item $\pubaux \getsr \Sim(|S|)$.
\item Return $A(\pubaux)$.
\end{enumerate}
Moreover, the probability with which $A$ outputs~1 in this experiment is
precisely $\Prob{\ExpPrivSSsim{\setprim,{\sf leak}}{A, \Sim}=1}$.
This completes the proof. \hfill\qed
\end{proof}

### 2016-09-30 results.tex
cheers
GBF correctness for private M
GBF, adding descriptive names to theorem statements in Section 4

\begin{theorem}\label{thm3}\label{thm:bf-ow}
Fix $k,m,n,r>0$, a set~$\elts$, and let $\setprim_{\mathrm{Bloom}}= (\Rep, \Qry)$ be the classical Bloom filter data structure over~$\elts$. Let $\distr{}{}$ be a distribution over subsets of universe~$\univ=2^\elts$, where $\mu = H_\infty(\distr{}{})$.  For any adversary~$A$ that makes $q$~queries to its oracle
\[
\AdvPrivOW{\setprim_{\mathrm{Bloom}},\distr{}{},r}{A} \leq  \frac{(kqn+n)}{2^{\mu}}
\]
\end{theorem}
\todo{Typeset simple proof.  Result is on chalkboard.}

@@

\begin{theorem}\label{thm2}\label{thm:ds-correctness}
Fix $k,m,n,r>0$, a set~$\elts$, and let $\setprim_{\mathrm{ds}}= (\Rep, \Qry)$ be the set-membership data structure (over~$\elts$) in Figure~\ref{fig:lin-and-ds}.  For any adversary~$A$ that makes a total of~$q$ queries to its oracle and has time-complexity~$O(t)$, there exists a prf-adversary ~$B$ (explicitly constructed in the proof of this theorem) such that
\[
\AdvCorrect{\setprim_{\mathrm{ds}},r}{A} \leq  \AdvPRF{F}{B}  + {\dbinom{q}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r\,.
\]
Here, $B$ asks $q$ queries, and has time complexity $O(t+qm)$.
\end{theorem}

\heading{Privacy. }
The privacy of $\setprim_{\mathrm{ds}}$ follows directly from our general result, Theorem~\ref{thm:xxx}.
\begin{theorem}\label{thm:ds-ss}
Fix $k,m,n>0$, a set~$\elts$, and let $\setprim_{\mathrm{ds}}= (\Rep, \Qry)$ be the set-membership data structure described in Figure~\ref{fig:lin-and-ds}.  For any set~$S \in 2^\elts$, let $\leak(S)=|S|$.  There exists a simulator~$\Sim$ and adversary~$B$ such that, for any adversary~$A$
\[
\AdvPrivSS{\setprim_{\mathrm{ds}},\leak}{A,\Sim} \leq  \AdvPRF{F}{B}
\]
%(Both~$B$ and~$\Sim$ are explicitly constructed in the proof of this theorem.)
\end{theorem}
\begin{proof}
It suffices to give the decomposition of $\Rep$ in to $\Rep_1$ and $\Rep_2$ as required by Theorem~\ref{thm:xxx}.
On input a set of distinct elements $S=\{x_1,x_2,\ldots,x_n\}$, algorithm~$\Rep_1$ returns $s_1=\langle 1,x_1 \rangle, s_2=\langle 2,x_1 \rangle, \ldots, s_k\langle k,x_1\rangle, s_{k+1}=\langle 1,x_2\rangle, \ldots, s_{2k}=\langle k,x_2\rangle, \ldots ,s_{kn+1}=\langle 1,x_n\rangle, \ldots, s_{kn}=\langle k,x_n \rangle$.  On input $n,F_K(s_1),\ldots,F_K(s_{kn})$, algorithm $\Rep_2$ simply initializes an all-zero array~$M$ of~$m$-bits, and sets the positions $M[F_K(s_i)]$ to 1.  It returns~$M$ as $\pubaux$.
\end{proof}

@@

\begin{theorem}\label{thm1}\label{thm:lin-correctness}
Fix $k,m,n,r>0$, a set~$\elts$, and let $\setprim_{\mathrm{lin}}= (\Rep, \Qry)$ be the set-membership data structure (over~$\elts$) described in Figure~\ref{fig:lin-and-bin-lin}.  For any adversary~$A$ that makes a total of~$q$ queries to its oracle and has time-complexity~$O(t)$, there exist prf-adversaries~$B_1,B_2$ (explicitly constructed in the proof of this theorem) such that
\[
\AdvCorrect{\setprim_{\mathrm{lin}},r}{A} \leq  \AdvPRF{F}{B_1} + \AdvPRF{F}{B_2}  +{\dbinom{q}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r\,.
\]
Here, $B_1$ and $B_2$, each ask~$q$ oracle queries and have time complexity~$O(t+qm)$.
\end{theorem}
The proof appears in Appendix~\ref{app:xxx}.  We note that Kirsch and Mitzenmacher~\cite{xxx} show
that the ($r=1$, zero-query) FP-probability for~$\setprim_\mathrm{lin}$ is
always within $O(1/n)$ of $(1-e^{-kn/m})^k$, although the asymptotic
rate of convergence is faster than~$1/n$.   As in previous cases, the multiplicative term $\dbinom{q}{r}$ arises when switching from the adaptive to zero-query settings.

\heading{Privacy. }
The SS-privacy of the linear-PRF hash construction follows directly from~Theorem~\ref{thm:xxx}.
\begin{theorem}\label{thm:lin-privacy}
Fix $k,m,n,r>0$, a set $\elts$, and let $\setprim_{\mathrm{lin}}= (\Rep, \Qry)$ be the set-membership data structure (over~$\elts$) described in Figure~\ref{fig:lin-and-bin-lin}. For any set~$S \in 2^{\elts}$, let $\leak(S)=|S|$.  There exists a simulator~$\Sim$ and an adversary~$B$ such that, for any adversary~$A$
\[
\AdvPrivSS{\setprim_{\mathrm{ds}},\leak}{A,\Sim} \leq  \AdvPRF{F}{B}
\]
%(Both~$B$ and~$\Sim$ are explicitly constructed in the proof of this theorem.)
\end{theorem}
\begin{proof}
It suffices to give the decomposition of $\Rep$ in to $\Rep_1$ and $\Rep_2$ as required by Theorem~\ref{thm:xxx}.
On input a set of distinct elements
$S=\{x_1,x_2,\ldots,x_n\}$, algorithm~$\Rep_1$ returns $s_1=\langle 1,x_1 \rangle, s_2=\langle 2,x_1 \rangle, s_3 = \langle 1,x_2\rangle, s_4=\langle 2,x_2 \rangle,\ldots,s_{2n-1}=\langle 1,x_n \rangle, s_{2n}=\langle 2,x_n \rangle$.

@@

\begin{theorem}\label{thm:bi-lin-ss}
Let $\setprim_{\bilin}= (\Rep, \Qry)$ be the set-membership data structure described in Figure~\ref{fig:neidermayer}, but instantiated with $F_{K}$ replaced by a random functions~$\rho$.  Let $\leak_{\mathsf{abl}}$ be the leakage function just described.   Let~$\elts=\{\mathrm{a,b,c}\}^*$. Let $n=3$,  $m=3\alpha $ for integer $\alpha >> 1$, and let, $k = \lceil \ln(2) \alpha \rceil$.\tsnote{This value of~$k$ is from the classical analysis for minimizing the FP rate for a Bloom filter, and is set this way for compatibility with classical results.  It isn't used in any essential way in the proof sketch.}  Let~$A$ be the adversary in Figure~\ref{fig:adv-bi-lin-ss}.  Then for any simulator $\Sim$, the advantage $\AdvPrivSS{\setprim_{\bilin},\leak_{\mathsf{abl}}}{A,\Sim}$ can be made arbitrarily close to $1/2$ by choice of~$\alpha$.
\end{theorem}
\begin{proof}(Sketch.)
On input the set~$S$ produced by~$A$, the $\Rep$ algorithm turns $x_1=$'cab', $x_2=$'bab' and $x_3$ into their respective bigram sets: $B_{x_1}=\{\sqcup\mathrm{c},\mathrm{ca},\mathrm{ab},\mathrm{b}\sqcup\}$, $B_{x_2}=\{\sqcup\mathrm{b},\mathrm{ba},\mathrm{ab}, \mathrm{b}\sqcup \}$; the set $B_{x_3}$ will be either $\{\sqcup\mathrm{c},\mathrm{ca},\mathrm{ab},\mathrm{ba}, \mathrm{a}\sqcup\}$, or $\{\sqcup\mathrm{c},\mathrm{ca},\mathrm{ab},\mathrm{bc}, \mathrm{c}\sqcup\}$, each with probability 1/2.  It then produces $\alpha$-bit arrays $M_1, M_2, M_3$ by hashing the corresponding bigram sets using the hash functions $h_j(s)=\rho_1(s)+ j\rho_2(s) \bmod m$.  Note that for sufficiently large~$m$, each of $M_1,M_2$ will contain exactly $4k$ positions set to 1; this is with overwhelming probability, up to collisions in the hash functions for different bigrams within a given bigram set.  Likewise, $M_{1,2}=M_1 \vee M_2$ will have exactly $6k$ positions set to 1, because $B_{x_1}$ and $B_{x_2}$ share $\mathrm{ab}$ and $\mathrm{a}\sqcup$.

@@

\begin{theorem}\label{thm:bi-ds-ss}
Let $\setprim_{\bilin}= (\Rep, \Qry)$ be the set-membership data structure described in Figure~\ref{fig:neidermayer}, but instantiated with $F_{K}$ replaced by a random functions~$\rho$.  Let $\leak$ be the leakage function described just prior to Theorem~\ref{thm:bi-lin-ss}.   Let~$\elts=\{\mathrm{a,b,c}\}^*$. Let $n=3$,  $m=3\alpha $ for integer $\alpha >> 1$, and let, $k = \lceil \ln(2) \alpha \rceil$.\tsnote{This value of~$k$ is from the classical analysis for minimizing the FP rate for a Bloom filter, and is set this way for compatibility with classical results.  It isn't used in any essential way in the proof sketch.}  Let~$A$ be the adversary in Figure~\ref{fig:adv-bi-lin-ss}.  Then for any simulator $\Sim$,
the advantage $\AdvPrivSS{\setprim_{\mathrm{ds}},\leak}{A,\Sim}$ can be made arbitrarily close to $1/2$ by choice of~$\alpha$.
\end{theorem}

@@

Finally, we observe that a similar version of the correctness attack
works outside of the ROM, say, when we hash via $H(j,x)=F_K(\langle
j,x \rangle)$ and assume~$F_K$ is a secure PRF.  Here, $\privaux=K$.  Now,
however, the work switches from offline hash evaluations (i.e., random
oracle calls) to online set-membership (i.e., $\TestOracle$) queries.

Switching now to the case of a \emph{private}~$M$ GBF, i.e., $\pubaux=\emptystring, \privaux=\langle M \rangle$, we have the
following correctness bound.

\begin{theorem}\fixme{FINISH! (Animesh?)}
Fix $k,m,n,r,\lambda>0$, and let $\setprim_{\mathrm{gbf}}=(\Rep, \Qry)$ be the private~$M$ garbled Bloom filter. For any adversary~$A$ that makes a total of~$q_T$ queries to the $\Test$ oracle, and $q_R$ queries to the RO, and has time-complexity~$O(t)$,
\[
\AdvCorrect{\setprim_{\mathrm{gbf}},r}{A} \leq  [...]
\]
\end{theorem}

@@

\begin{theorem}
Fix $k,m,n,r,\lambda>0$, and let $\setprim_{\mathrm{gbf}}=(\Rep, \Qry)$ be the public~$M$ garbled Bloom filter, in the random-oracle model for~$H$.  Then 
\[
\AdvPrivOW{\setprim_{\mathrm{gbf}},\distr{}{}}{A_{\mathrm{ow}}} \geq 1 - \left(1-\frac{1}{2^{\mu}} \right)^{q} \geq 1 - e^{-q/2^\mu}
\]
 where $\mu = H_\infty(\distr{}{})$ is the pointwise min-entropy of~$\distr{}{}$, and $A_{\mathrm{ow}}$ makes $kq$ random-oracle queries.
\end{theorem}

\todo{If time:  would be great to have an upperbound on onewayness for this construction!}

If instantiated with hash functions $H_j(x) = F_K(\langle j,x \rangle)$ and $\privaux = \langle K \rangle$, the SS-privacy of the GBF follows directly from~Theorem~\ref{thm:xxx}.
\begin{theorem}\label{thm:gbf-prf-privacy}
Fix $k,m,n,r,\lambda>0$ and a function family~$F\colon \calK \times \bits^* \to [m]$.  Let $\setprim_{\mathrm{gbf\mbox{-}prf}}= (\Rep, \Qry)$ be the garbled Bloom filter with hash functions $H_j(x)=F_K(\langle j,x \rangle)$ and $\privaux=\langle K \rangle$.  For any set~$S$, let $\leak(S)=|S|$.  There exists a simulator~$\Sim$ and an adversary~$B$ such that, for any adversary~$A$
\[
\AdvPrivSS{\setprim_{\mathrm{gbf\mbox{-}prf}},\leak}{A,\Sim} \leq  \AdvPRF{F}{B}
\]
%(Both~$B$ and~$\Sim$ are explicitly constructed in the proof of this theorem.)
\end{theorem}
\begin{proof}
It suffices to give the decomposition of $\Rep$ in to $\Rep_1$ and $\Rep_2$ as required by Theorem~\ref{thm:xxx}.
On input a set of distinct elements $S=\{x_1,x_2,\ldots,x_n\}$, algorithm~$\Rep_1$ returns $s_1=\langle 1,x_1 \rangle, s_2=\langle 2,x_1 \rangle, \ldots, s_k\langle k,x_1\rangle, s_{k+1}=\langle 1,x_2\rangle, \ldots, s_{2k}=\langle k,x_2\rangle, \ldots ,s_{kn+1}=\langle 1,x_n\rangle, \ldots, s_{kn}=\langle k,x_n \rangle$.  On input $n,F_K(s_1),\ldots,F_K(s_{kn})$, algorithm $\Rep_2$ carries out the pseudocode of~$\Rep$ in Figure~\ref{fig:gbf}, making use of $F_K(s_1),\ldots,F_K(s_{kn})$ in the obvious way.  It returns~$M$ as $\pubaux$.
\end{proof}

>>>>

\begin{theorem}[{\rm OW-privacy of classic BF in the ROM}]\label{thm3}\label{thm:bf-ow}
Fix $k,m,n,r>0$, a set~$\elts$, and let $\setprim_{\mathrm{Bloom}}= (\Rep, \Qry)$ be the classical Bloom filter data structure over~$\elts$. Let $\distr{}{}$ be a distribution over subsets of universe~$\univ=2^\elts$, where $\mu = H_\infty(\distr{}{})$.  For any adversary~$A$ that makes $q$~queries to its oracle
\[
\AdvPrivOW{\setprim_{\mathrm{Bloom}},\distr{}{},r}{A} \leq  \frac{(kqn+n)}{2^{\mu}}
\]
\end{theorem}
\todo{Typeset simple proof.  Result is on chalkboard.}

@@

\begin{theorem}[{\rm Correctness of DS-PRF}]\label{thm2}\label{thm:ds-correctness}
Fix $k,m,n,r>0$, a set~$\elts$, and let $\setprim_{\mathrm{ds}}= (\Rep, \Qry)$ be the set-membership data structure (over~$\elts$) in Figure~\ref{fig:lin-and-ds}.  For any adversary~$A$ that makes a total of~$q$ queries to its oracle and has time-complexity~$O(t)$, there exists a prf-adversary ~$B$ (explicitly constructed in the proof of this theorem) such that
\[
\AdvCorrect{\setprim_{\mathrm{ds}},r}{A} \leq  \AdvPRF{F}{B}  + {\dbinom{q}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r\,.
\]
Here, $B$ asks $q$ queries, and has time complexity $O(t+qm)$.
\end{theorem}

\heading{Privacy. }
The privacy of $\setprim_{\mathrm{ds}}$ follows directly from our general result, Theorem~\ref{thm:xxx}.
\begin{theorem}[\rm{SS-privacy of DS PRF}]\label{thm:ds-ss}
Fix $k,m,n>0$, a set~$\elts$, and let $\setprim_{\mathrm{ds}}= (\Rep, \Qry)$ be the set-membership data structure described in Figure~\ref{fig:lin-and-ds}.  For any set~$S \in 2^\elts$, let $\leak(S)=|S|$.  There exists a simulator~$\Sim$ and adversary~$B$ such that, for any adversary~$A$
\[
\AdvPrivSS{\setprim_{\mathrm{ds}},\leak}{A,\Sim} \leq  \AdvPRF{F}{B}
\]
%(Both~$B$ and~$\Sim$ are explicitly constructed in the proof of this theorem.)
\end{theorem}
\begin{proof}
It suffices to give the decomposition of $\Rep$ in to $\Rep_1$ and $\Rep_2$ as required by Theorem~\ref{thm:xxx}.
On input a set of distinct elements $S=\{x_1,x_2,\ldots,x_n\}$, algorithm~$\Rep_1$ returns $s_1=\langle 1,x_1 \rangle, s_2=\langle 2,x_1 \rangle, \ldots, s_k\langle k,x_1\rangle, s_{k+1}=\langle 1,x_2\rangle, \ldots, s_{2k}=\langle k,x_2\rangle, \ldots ,s_{kn+1}=\langle 1,x_n\rangle, \ldots, s_{kn}=\langle k,x_n \rangle$.  On input $n,F_K(s_1),\ldots,F_K(s_{kn})$, algorithm $\Rep_2$ simply initializes an all-zero array~$M$ of~$m$-bits, and sets the positions $M[F_K(s_i)]$ to 1.  It returns~$M$ as $\pubaux$.
\end{proof}

@@

\begin{theorem}[{\rm Correctness of linear-PRF}]\label{thm1}\label{thm:lin-correctness}
Fix $k,m,n,r>0$, a set~$\elts$, and let $\setprim_{\mathrm{lin}}= (\Rep, \Qry)$ be the set-membership data structure (over~$\elts$) described in Figure~\ref{fig:lin-and-bin-lin}.  For any adversary~$A$ that makes a total of~$q$ queries to its oracle and has time-complexity~$O(t)$, there exist prf-adversaries~$B_1,B_2$ (explicitly constructed in the proof of this theorem) such that
\[
\AdvCorrect{\setprim_{\mathrm{lin}},r}{A} \leq  \AdvPRF{F}{B_1} + \AdvPRF{F}{B_2}  +{\dbinom{q}{r}} \left( (1-e^{-kn/m})^k + O(1/n) \right)^r\,.
\]
Here, $B_1$ and $B_2$, each ask~$q$ oracle queries and have time complexity~$O(t+qm)$.
\end{theorem}
The proof appears in Appendix~\ref{app:xxx}.  We note that Kirsch and Mitzenmacher~\cite{xxx} show
that the ($r=1$, zero-query) FP-probability for~$\setprim_\mathrm{lin}$ is
always within $O(1/n)$ of $(1-e^{-kn/m})^k$, although the asymptotic
rate of convergence is faster than~$1/n$.   As in previous cases, the multiplicative term $\dbinom{q}{r}$ arises when switching from the adaptive to zero-query settings.

\heading{Privacy. }
The SS-privacy of the linear-PRF hash construction follows directly from~Theorem~\ref{thm:xxx}.
\begin{theorem}[{\rm SS-privacy of linear-PRF}]\label{thm:lin-privacy}
Fix $k,m,n,r>0$, a set $\elts$, and let $\setprim_{\mathrm{lin}}= (\Rep, \Qry)$ be the set-membership data structure (over~$\elts$) described in Figure~\ref{fig:lin-and-bin-lin}. For any set~$S \in 2^{\elts}$, let $\leak(S)=|S|$.  There exists a simulator~$\Sim$ and an adversary~$B$ such that, for any adversary~$A$
\[
\AdvPrivSS{\setprim_{\mathrm{ds}},\leak}{A,\Sim} \leq  \AdvPRF{F}{B}
\]
%(Both~$B$ and~$\Sim$ are explicitly constructed in the proof of this theorem.)
\end{theorem}
\begin{proof}
It suffices to give the decomposition of $\Rep$ in to $\Rep_1$ and $\Rep_2$ as required by Theorem~\ref{thm:xxx}.
On input a set of distinct elements
$S=\{x_1,x_2,\ldots,x_n\}$, algorithm~$\Rep_1$ returns $s_1=\langle 1,x_1 \rangle, s_2=\langle 2,x_1 \rangle, s_3 = \langle 1,x_2\rangle, s_4=\langle 2,x_2 \rangle,\ldots,s_{2n-1}=\langle 1,x_n \rangle, s_{2n}=\langle 2,x_n \rangle$.

@@

\begin{theorem}[{\rm SS-privacy of bigram linear-PRF}]\label{thm:bi-lin-ss}
Let $\setprim_{\bilin}= (\Rep, \Qry)$ be the set-membership data structure described in Figure~\ref{fig:neidermayer}, but instantiated with $F_{K}$ replaced by a random functions~$\rho$.  Let $\leak_{\mathsf{abl}}$ be the leakage function just described.   Let~$\elts=\{\mathrm{a,b,c}\}^*$. Let $n=3$,  $m=3\alpha $ for integer $\alpha >> 1$, and let, $k = \lceil \ln(2) \alpha \rceil$.\tsnote{This value of~$k$ is from the classical analysis for minimizing the FP rate for a Bloom filter, and is set this way for compatibility with classical results.  It isn't used in any essential way in the proof sketch.}  Let~$A$ be the adversary in Figure~\ref{fig:adv-bi-lin-ss}.  Then for any simulator $\Sim$, the advantage $\AdvPrivSS{\setprim_{\bilin},\leak_{\mathsf{abl}}}{A,\Sim}$ can be made arbitrarily close to $1/2$ by choice of~$\alpha$.
\end{theorem}
\begin{proof}\tsnote{still a bit sketchy but believable}
On input the set~$S$ produced by~$A$, the $\Rep$ algorithm turns $x_1=$'cab', $x_2=$'bab' and $x_3$ into their respective bigram sets: $B_{x_1}=\{\sqcup\mathrm{c},\mathrm{ca},\mathrm{ab},\mathrm{b}\sqcup\}$, $B_{x_2}=\{\sqcup\mathrm{b},\mathrm{ba},\mathrm{ab}, \mathrm{b}\sqcup \}$; the set $B_{x_3}$ will be either $\{\sqcup\mathrm{c},\mathrm{ca},\mathrm{ab},\mathrm{ba}, \mathrm{a}\sqcup\}$, or $\{\sqcup\mathrm{c},\mathrm{ca},\mathrm{ab},\mathrm{bc}, \mathrm{c}\sqcup\}$, each with probability 1/2.  It then produces $\alpha$-bit arrays $M_1, M_2, M_3$ by hashing the corresponding bigram sets using the hash functions $h_j(s)=\rho_1(s)+ j\rho_2(s) \bmod m$.  Note that for sufficiently large~$m$, each of $M_1,M_2$ will contain exactly $4k$ positions set to 1; this is with overwhelming probability, up to collisions in the hash functions for different bigrams within a given bigram set.  Likewise, $M_{1,2}=M_1 \vee M_2$ will have exactly $6k$ positions set to 1, because $B_{x_1}$ and $B_{x_2}$ share $\mathrm{ab}$ and $\mathrm{a}\sqcup$.

@@

\begin{theorem}[{\rm SS-privacy of bigram DS PRF-hash}]\label{thm:bi-ds-ss}
Let $\setprim_{\bilin}= (\Rep, \Qry)$ be the set-membership data structure described in Figure~\ref{fig:neidermayer}, but instantiated with $F_{K}$ replaced by a random functions~$\rho$.  Let $\leak$ be the leakage function described just prior to Theorem~\ref{thm:bi-lin-ss}.   Let~$\elts=\{\mathrm{a,b,c}\}^*$. Let $n=3$,  $m=3\alpha $ for integer $\alpha >> 1$, and let, $k = \lceil \ln(2) \alpha \rceil$.\tsnote{This value of~$k$ is from the classical analysis for minimizing the FP rate for a Bloom filter, and is set this way for compatibility with classical results.  It isn't used in any essential way in the proof sketch.}  Let~$A$ be the adversary in Figure~\ref{fig:adv-bi-lin-ss}.  Then for any simulator $\Sim$,
the advantage $\AdvPrivSS{\setprim_{\mathrm{ds}},\leak}{A,\Sim}$ can be made arbitrarily close to $1/2$ by choice of~$\alpha$.
\end{theorem}

@@

Finally, we observe that a similar version of the correctness attack
works outside of the ROM, say, when we hash via $H(j,x)=F_K(\langle
j,x \rangle)$ and assume~$F_K$ is a secure PRF.  Here,
$\privaux=\langle K \rangle$.  Now,
however, the work switches from offline hash evaluations (i.e., random
oracle calls) to online set-membership (i.e., $\TestOracle$) queries.

Switching now to the case of a \emph{private}-$M$ GBF, i.e., $\pubaux=\emptystring, \privaux=\langle M \rangle$, we have the
following correctness bound.

\begin{theorem}[{\rm Correctness of private-$M$ GBF in the ROM}]\fixme{FINISH! (Animesh?)}
Fix $k,m,n,r,\lambda>0$, and let $\setprim_{\mathrm{gbf}}=(\Rep, \Qry)$ be the private-$M$ garbled Bloom filter. For any adversary~$A$ that makes a total of~$q_T$ queries to the $\Test$ oracle, and $q_R$ queries to the RO, and has time-complexity~$O(t)$,
\[
\AdvCorrect{\setprim_{\mathrm{gbf}},r}{A} \leq  {\dbinom{q_T}{r}} \left( \dfrac{1}{2^{\lambda}} \right)^r\,.
\]
\end{theorem}

@@

\begin{theorem}[{\rm OW-privacy of public-$M$ GBF}]
Fix $k,m,n,r,\lambda>0$, and let $\setprim_{\mathrm{gbf}}=(\Rep, \Qry)$ be the public-$M$ garbled Bloom filter, in the random-oracle model for~$H$.  Then \fixme{This probability might not be correct... verify when less tired.}
\[
\AdvPrivOW{\setprim_{\mathrm{gbf}},\distr{}{}}{A_{\mathrm{ow}}} \geq 1 - \left(1-\frac{n}{2^{\mu}} \right)^{q} \geq 1 - e^{-nq/2^\mu}
\]
 where $\mu = H_\infty(\distr{}{})$ is the pointwise min-entropy of~$\distr{}{}$, and $A_{\mathrm{ow}}$ makes $kq$ random-oracle queries.
\end{theorem}
\noindent
We conjecture that this is the optimal attack on the GBF in this setting.

If instantiated with hash functions $H_j(x) = F_K(\langle j,x \rangle)$ and $\privaux = \langle K \rangle$, the SS-privacy of the GBF follows directly from~Theorem~\ref{thm:xxx}.
\begin{theorem}[{\rm SS-privacy of GBF with secret hash functions}]
\label{thm:gbf-prf-privacy}
Fix $k,m,n,r,\lambda>0$ and a function family~$F\colon \calK \times \bits^* \to [m]$.  Let $\setprim_{\mathrm{gbf\mbox{-}prf}}= (\Rep, \Qry)$ be the garbled Bloom filter with hash functions $H_j(x)=F_K(\langle j,x \rangle)$ and $\privaux=\langle K \rangle$.  For any set~$S$, let $\leak(S)=|S|$.  There exists a simulator~$\Sim$ and an adversary~$B$ such that, for any adversary~$A$
\[
\AdvPrivSS{\setprim_{\mathrm{gbf\mbox{-}prf}},\leak}{A,\Sim} \leq  \AdvPRF{F}{B}
\]
%(Both~$B$ and~$\Sim$ are explicitly constructed in the proof of this theorem.)
\end{theorem}
\begin{proof}
It suffices to give the decomposition of $\Rep$ in to $\Rep_1$ and $\Rep_2$ as required by Theorem~\ref{thm:xxx}.
On input a set of distinct elements $S=\{x_1,x_2,\ldots,x_n\}$, algorithm~$\Rep_1$ returns $s_1=\langle 1,x_1 \rangle, s_2=\langle 2,x_1 \rangle, \ldots, s_k\langle k,x_1\rangle, s_{k+1}=\langle 1,x_2\rangle, \ldots, s_{2k}=\langle k,x_2\rangle, \ldots ,s_{kn+1}=\langle 1,x_n\rangle, \ldots, s_{kn}=\langle k,x_n \rangle$.  On input $n,F_K(s_1),\ldots,F_K(s_{kn})$, algorithm $\Rep_2$ carries out the pseudocode of~$\Rep$ in Figure~\ref{fig:gbf}, making use of $F_K(s_1),\ldots,F_K(s_{kn})$ in the obvious way.  It returns~$M$ as $\pubaux$.
\end{proof}
